Unfolding the City: Spatial Preference Based on Individual Characteristics

### 2019-12-31 ia/ia_vis_3d.tex
latex manu

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}

\usepackage{mathptmx}

\usepackage{times}

\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

\usepackage{url}
\usepackage{ulem}

\usepackage{color, xcolor}
\definecolor{darkg}{rgb}{0,0.6,0}
\definecolor{lgreen}{rgb}{0,0.8,0}
\definecolor{purple}{rgb}{0.93,0.48,0.03}
\definecolor{orange}{rgb}{0.43,0.48,0.03}
% \ifdraft
%Our comments:
\newcommand{\lmc}[1]{{\color{lgreen}[LM: #1]}}
\newcommand{\wqc}[1]{{\color{orange}[WQ: #1]}}

%Noticable new adds:
\newcommand{\wq}[1]{{\color{blue}#1}}
\newcommand{\lm}[1]{{\color{darkg}#1}}

\newcommand{\m}{\textcolor{black}}

\usepackage{multirow}
\usepackage{tabularx}

\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage[misc]{ifsym}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Social Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Qi Wang \and Min Lu \and Yang Yue \and Qingquan Li}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Q. Wang \and Q. Li(\Letter) \at
              the State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan, China, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
              Tel.: +86-13297983047\\
              \email{wangqi@whu.edu.cn}, {liqq@szu.edu.cn}           %  \\
           \and M. Lu \and Y. Yue \at
              School of Architecture and Urban Planning, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
              \email{minlu@szu.edu.cn}, {yueyang@szu.edu.cn}           %  \\
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns. Different from the well study of anonymous travel behaviors, the mobility patterns of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.

\keywords{Visual analytics \and mobility pattern \and individual characteristics \and city }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
\wqc{change mobility pattern to spatial attractiveness}
The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities. Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}. Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

In the past decades, the power of visual analytics in exploring spatial-temporal data has been recognized and well developed. Transportation problems are answered by various movement data, such as traffic jams in taxi GPS trajectoires~\citep{wang2013visual}, interchanging flows in public transportation~\citep{zeng2013visualizing}, etc. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\citep{chen2017map} or topics~\citep{bosch2013scatterblogs2}. Those works essentially contribute in deepening the contextual understanding of moving activity. But they rarely combine the mobility with individuals' characteristics because which cannot be 100\% inferred from social media profiles. There is still a research gap in exploring the relationship between mobility pattern and characteristics.

In this work, we contextualize the analysis of mobility pattern in the backcloth of individual characteristics. Our motivation is to fuse the movement data with individuals' profiles in an attempt to ascertain the dynamics pattern of groups with different characteristics. To this, we need to get the characterized information of movers. The sensitivity issue in privacy data is one of the main challenges. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to count information online. In this work, with a census survey released via social media application, we ran an online demographical collection campaign. Then we developed a visual analytics system to explore the mobility patterns centered around people. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the mobility patterns. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method. There are two contributions of this work:

@@

\section{Related work}

This work concerns the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\citep{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

\subsection{Movement data analysis}
 With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mine trajectory~\citep{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\citep{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\citep{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\citep{guo2011tripvista} and Zeng et al.~\citep{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\citep{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking. For multiple routes, Liu et al.~\citep{liu2011_routediversity} study the route diversity between locations and Lu et al.~\citep{Lu2017_multipleroute} explore the route choice behavior among multiple routes.

\subsection{Geo-tagged Social Media Data Analysis}
As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives. As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\citep{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\citep{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places. Krueger et al.~\citep{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\citep{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media. Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\citep{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\citep{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, the wrong inferring is inevitable. Longley et al.~\citep{Longley2015}~\citep{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

\section{Online Census}
The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data from the social media source. Complementary to the conventional census, it brings the benefit of larger sampling frequency and a broader range in terms of space and time. It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/survey_app}
 \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page}
 \label{fig:app}
\end{figure}

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolia in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_over}
 \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns}
 \label{fig:data_over}
\end{figure}

\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and demographic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)). Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).

\subsection{Basic Statistics of Data}

Over the releasing time period from \m{2015-11 to 2016-01}, 21435 individuals (48\% females and 52\% males) were reached and \m{229155} trips are collected. Each volunteer contributes \m{11} trips average.

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\citep{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data1}
 \caption{Age and Education Distribution: (a) age; (b) education}
 \label{fig:data_age_edu}
\end{figure}

Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of ages, dominating between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate.

@@

Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. The covering of jobs is pretty wide. Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200 000. Individuals with higher salary are also reached in our census.

@@

Figure~\ref{fig:data_geometry} shows the basic statistics related to trips. In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life. There are obvious morning and late afternoon peaks. Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\citep{batty2013new}.

% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc. The diverse purposes make it possible to characterize the flows across the city between different functional places.

@@

\section{Overview}
\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}

\subsection{Goal}

\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
\wq{Spatial attractiveness is an important concept in GIS. Explain why. To derive the details, we interview the expert in GIS. Some questions like, how citizens live in the city, where they live, work and entertain? Which place is popular? For different citizens, whether a place has the same attraction? ... With these questions, we summarize them into the tasks below, which need to be answered by our system.} \lm{Below are some core research concerns derived from domain exports.}

\textbf{Spatial Attractiveness} \lmc{Can we find some reference about Spatial Attractiveness. If not, we can give an explaination by ourselves.}

\textbf{Attractiveness Diversity} \lmc{Same...}

\textbf{Attractiveness Differences} \lmc{Same...}

@@

\lm{The exploration of core concepts above are resolved further with following tasks... to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city.
\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\end{itemize}

@@

\begin{itemize}
\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.
\item \textit{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\citep{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
\item \textit{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information.
\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
\end{itemize}

% Classification method, flow clustering method, Semantic representation.

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}

\ifCLASSOPTIONcompsoc
\usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
\else
\usepackage[caption=false, font=footnotesize]{subfig}
\fi

\ifCLASSINFOpdf
   \usepackage{graphicx}
   \usepackage{lipsum}
   \usepackage{booktabs}
   \usepackage{threeparttable}
   \usepackage{caption}
   \usepackage{epstopdf}
   \usepackage{cite}
\else
\fi

\usepackage{xcolor}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI-}

\title{Unfolding the City: Spatial Preference Based on Individual Characteristics}

\author{\uppercase{Qi wang}\authorrefmark{1,2}, \uppercase{min lu}\authorrefmark{2,3} and \uppercase{Qingquan Li}\authorrefmark{1,2}}
\address[1]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430072, China}
\address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
\address[3]{School of Architecture and Urban Planning, ShenZhen University, Shenzhen 518060, China}

\tfootnote{This work was jointly supported by the National Natural Science Foundation of China(No. 71961137003 and No. 41671387).}

\markboth
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

\corresp{Corresponding author: Qingquan Li (e-mail: liqq@szu.edu.cn).}

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual social characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns. Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.\end{abstract}

\begin{keywords}
Visual analytics, spatial preference, individual characteristics, data collection
\end{keywords}

\titlepgskip=-15pt

@@

\section{Introduction}
\label{sec:introduction}
\PARstart{T}{he} science fiction \textbf{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people prefer to select different places according to individual characteristics, such as social, economic, educational features. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\cite{pahl1975whose} posed the question "whose city" and interest in understanding the territorial inequalities. Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}. Having a good understanding of relationships between the spatial attractiveness and the characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

In the past decades, the power of visual analytics in exploring spatiotemporal data has been recognized and well developed. Various urban problems are answered, such as traffic jams~\cite{wang2013visual}, interchanging flows in public transportation~\cite{zeng2013visualizing}, etc. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\cite{chen2017map} or topics~\cite{bosch2013scatterblogs2}. Those works essentially contribute in deepening the contextual understanding of moving activity. However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles. One of the main challenges is the sensitivity issue in privacy data. There is still a research gap in exploring the relationship between spatial pattern and social characteristics.

In this work, we contextualize the analysis of citizens' spatial distribution in the backcloth of individual characteristics. With the motivation of fusing the movement data with individuals' profiles in an attempt to ascertain the spatial distribution for groups with different characteristics, we need to get the characterized information of movers. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to count information online. In this work, with a census survey released via social media application, we ran an online demographical collection campaign. Based on the data collected, we developed a visual analytics system to explore where do citizens prefer to go. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the distribution of movements. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method. There are two contributions of this work:

@@

\section{Related Work}
This work concerns the research topic of spatial data visual analytics. Spatiotemporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

\subsection{Movement data analysis}
With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mine trajectory~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes.

\subsection{Geo-tagged Social Media Data Analysis}
As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives. As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places. Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media. Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\cite{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, the wrong inferring is inevitable. Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

\section{motivation}

\label{sec:concept}
This work was sparked from a meeting with two domain experts who work on human mobility and urban informatics in the geospatial field. The experts pointed out that as big and open data evolved in, the scope of urban research has been lifted from the spatial perspective up to social-spatial perspective. There is a rising research interest in understanding how groups of citizens with certain social characteristics select places during their daily lives. Whether people visit places with preference which are intrinsically affected by their social-economic characteristics? Is there a limitation or probabilities of interaction between different socio-economic groups in public spaces? With the advances of data acquisition and analysis techniques, they demanded to go beyond the conventional static sampled questionnaires, which usually survey visiting preferences. They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive examination of spatial distribution in different contexts of social characteristics.

Thereafter we booted up this project with several rounds of discussions, to frame the research problem with two core contents and the research procedure. The first concepts is \textbf{Social Characteristics}.  Social characteristics of a person or group of citizens  are the descriptors which contribute to the specification of the populations. This work intends to cover the social characteristics from multi-facets, including descriptors such as gender, income, education, etc. The second content is \textbf{Spatial Distribution}. It is reflected by the popularity of a place to be visited.

Motivated by their research interest in understanding the spatial attractiveness with individual social characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.

\section{Data Description}
\label{subsec:pipeline}
Considering there is no existing public dataset could fit our topic well, this work is consolidated with a self-maintained data sourcing. We release an online data census to collect the social characteristics and movement logs of individuals for almost half a year. Then a series of statistical analysis is performed on the collected data for sampling bias checking.

\subsection{Online Census}

The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data by apps within the phones. Complementary to the conventional census, it brings the benefit of convenient collections without much manpower and precise spatial locations by GPS instead of semantic description. Meanwhile, it is possible to collective the movement in human inactive time, such as the mid-night.

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, the most widely used social media mobile application. Fig. \ref{fig:app} shows the data collecting interfaces. For privacy issue, all detailed personal information are desensitized to categorical levels. Considering the main aim on the relationship between spatial distribution of movements and individuals' characteristics, there are two crucial contents to be collected:

\textbf{Individual Characteristics} Fig. \ref{fig:data_over} lists the eight domains, including social, economic and demographic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires the information of start/end location, start/end time, traveling purpose. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/survey_app}
  \captionsetup{justification=centering}
 \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page.}
 \label{fig:app}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/data_over}
 \captionsetup{justification=centering}
 \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns.}
 \label{fig:data_over}
\end{figure}

\subsection{Statistics of Collected Data}

Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals (48\% females and 52\% males) participated in the census and 229,155 trips were collected. Each volunteer contributed 11 trips average.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data1}
 \caption{Age and Education Distribution: (a) age; (b) education.}
 \label{fig:data_age_edu}
\end{figure}

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their profile  and movements.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

Fig. \ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of ages, dominating between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate.

Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200,000. Individuals with higher salary are also reached in our census.

@@

Fig. \ref{fig:data_geometry} shows the basic statistics related to movements. In Fig. ~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life. There are obvious morning and late afternoon peaks. Fig. ~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Fig. ~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

@@

@@

\section{Visual Design}

The design of visual analytics system is iterated via multi-pass discussions with the two domain experts. In this section, we first introduce specific tasks the system intended for and design rationales aligned to provide the user-friendly interface for domain experts. Then we introduce the visual design.

@@

The exploration of core contents (introduced in Section~\ref{sec:concept}) is resolved further with the following tasks.

\begin{itemize}
\item \textbf{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textbf{Task 2: Explore the mobility distribution of a group}: to explore where, how and why an interested group go in the city.
\item \textbf{Task 3: Compare mobility distribution among multiple groups}: to know the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual characteristics.
\end{itemize}

\begin{figure*}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=18.1cm]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure*}

@@

\begin{itemize}
\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.
\item \textbf{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
\item \textbf{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
\item \textbf{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information.
\item \textbf{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textbf{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
\end{itemize}

\subsection{Visualizations}
\label{subsec:vis}

With those design considerations, we develop a visual analytics system as Fig. \ref{fig:teaser} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

\subsubsection{Data-driven Profile Visualization}
